\documentclass{article}

\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{verbatim}
\usepackage{algpseudocode}
\usepackage{natbib}
\usepackage{url}
\usepackage{listings}
\usepackage[spanish]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{float}
\usepackage{array}
\usepackage{booktabs}
\usepackage{amssymb}
%\setcounter{MaxMatrixCols}{16}


\begin{document}
\title{Report Lab 1}
\date {\today}
\author{Tatiana Lopez Guevara}
\maketitle


\section{Variables}
\subsection{Local vs Global}
A global variable can be accessed from any part of the program and will 
be alive during the execution of the whole program.
A local variable is only accessible inside the scope its 
declared and will be alive during the execution of the function or scope it lives in.

The section \ref{sec:fibo} shows the use of the global variable $\varphi$ that holds 
the known value of the golden ratio. Inside the function \verb|golden_ratio| 
the value $err$ is a local variable which is only accessible inside that function.

\subsection{Elementary functions}
In this section I created the functions \verb|mean, min, max| which received 2 
integer parameters. In this case the input variables do not need to be modified
and therefore I learned how to help a little bit the compiler by explicitly 
specifying the read only property with \verb+ const + keyword and also by not 
creating a copy by passing it a reference with \verb+ & +. 

\section{Combination}
\subsection{Factorial}
In this function we noticed 2 things besides the optimizations mentioned 
int the previous section:
\begin{itemize}
\item The Fibonacci is only defined for values in $\mathbb{N}^0$ and therefore
is better to declare it as unsigned. Due to the extremely fast growing of the
factorial function we declared the type as \verb+short+.
\item The return type must be able to hold a very large number. At the begining
we declared it as \verb+long long+ but then we realized that it overflowed with
the factorial of numbers greater than 21 and therefore we had to change it to
\verb+double+.
\end{itemize}

\subsection{Combinations}
In order to follow the KISS phylosphy, I just reused the 
\verb+factorial+ function created in the previous step to calculate $n!, k!$
and $(n-k)!$ used in the formula.

The number of combinations of a lottery game is $C^{49}_{6}$ and 
the program gave the result 1.39838e+07.

\subsection{Combinations with repetitions}
Same as before. I just reused the \verb+combinations+ function to get
the term:
\begin{equation*}
\binom{n+k-1}{k}
\end{equation*} 

\subsection{Permutations}
In this function I reused the two previous functions to 
get the value $P_5^{54} = 3.79501e+08$ from
the formula:

\begin{equation*}
P_k^n = \frac{n!}{(n-k)!} 
\end{equation*} 


\section{Fibonacci}
\label{sec:fibo}
The Fibonacci function has a recursive definition, however the implementation
realized here was not, first because for printing each one of the terms it was 
more easy and second because it is faster.

\subsection{Golden Ratio}

\section{Pascal's Triangle}
One of the most simple and effective ways to print the Pascal's triangle
is using arrays to calculate the current value only through sums and
based only on 2 previous factos. 
However, this was implemented for Lab2 and here I just used
another simple approach by just reusing the \verb+combinations+ function
for each calculation.

\section{Other things}
\subsection{String}
I used 5 ways to create strings: the default constructor, passing a string,
assigning a value with the \verb+ = + operator, and repeating a character 
constructor \cite{cpp}. 
The empty string was then assigned to the concatenated value of
the first 2 strings using the \verb|+| operator. The last string was
used to play with the \verb+append+ and \verb+insert+ functions. 
All values were shown in the output ussing the \verb+<<+ operator and
\verb+c_str()+ 

\subsection{Main}
The parameters of the main are used for accessing the information
of the parameters passed into the program on the invocation.
More specifically, \verb+argc+ is the number of parameters passed 
where the 1st one is the program invocation by itself.
\verb+argv+ is a vector of \verb+argc+ possitions, each one corresponding
to the value of the parameters for the program.

\bibliographystyle{plainnat}
\bibliography{biblio}

\end{document}
